Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-08-25 draftfinalreport_v4.Rnw
Minor edits to add risk units

\documentclass{article}
\PassOptionsToPackage{draft}{graphicx} % draft without figures
\usepackage{longtable}
\usepackage{times}
\usepackage{hyperref}
\usepackage{tikz}
%\usepackage{bibunits}
\usepackage{natbib}
\usepackage{graphics}
\usepackage{amsmath}
\usepackage{indentfirst}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{eurosym}
\usepackage{todonotes}
\usepackage{subfig}
\usepackage{enumitem}
\usepackage{pdflscape}
\usepackage{booktabs}
\usepackage{array}
\usepackage{rotating}
\usepackage{threeparttable}
\usepackage{blindtext}
\usepackage{dcolumn}
\usepackage{tabularx}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage{caption2}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{placeins}
\usepackage{framed}
\usepackage{float}
\usepackage{authblk}
\usepackage[maxfloats=50]{morefloats}
\newcommand{\vecA}{\mathbf{A}}
\newcommand{\vecB}{\mathbf{B}}
\newcommand{\vecC}{\mathbf{C}}
\newcommand{\vecD}{\mathbf{D}}
\newcommand{\vecE}{\mathbf{E}}
\newcommand{\vecF}{\mathbf{F}}
\newcommand{\vecH}{\mathbf{H}}
\newcommand{\vecI}{\mathbf{I}}
\newcommand{\vecJ}{\mathbf{J}}
\newcommand{\vecK}{\mathbf{K}}
\newcommand{\vecM}{\mathbf{M}}
\newcommand{\vecN}{\mathbf{N}}
\newcommand{\vecP}{\mathbf{P}}
\newcommand{\vecQ}{\mathbf{Q}}
\newcommand{\vecS}{\mathbf{S}}
\newcommand{\vecT}{\mathbf{T}}
\newcommand{\vecW}{\mathbf{W}}
\newcommand{\vecZ}{\mathbf{Z}}
\newcommand{\vecb}{\mathbf{b}}
\newcommand{\vecc}{\mathbf{c}}
\newcommand{\vece}{\mathbf{e}}
\newcommand{\vecf}{\mathbf{f}}
\newcommand{\vecg}{\mathbf{g}}
\newcommand{\vech}{\mathbf{h}}
\newcommand{\veci}{\mathbf{i}}
\newcommand{\vecr}{\mathbf{r}}
\newcommand{\vecu}{\mathbf{u}}
\newcommand{\vecv}{\mathbf{v}}
\newcommand{\vecw}{\mathbf{w}}
\newcommand{\vecx}{\mathbf{x}}
\newcommand{\vecy}{\mathbf{y}}
\newcommand{\vecz}{\mathbf{z}}
\newcommand{\Ach}{\mathcal{H}}
\newcommand{\Ell}{\mathcal{L}}
\newcommand{\En}{\mathcal{N}}
\newcommand{\Pe}{\mathcal{P}}
\newcommand{\Ro}{\mathcal{R}_0}
\newcommand{\Rc}{\mathcal{R}_c}
\newcommand{\Pv}{\mathcal{P}_v}
\newcommand{\Rr}{\mathcal{R}}
\newcommand{\Qu}{\mathcal{Q}}
\newcommand{\Te}{\mathcal{T}}
\newcommand{\Ve}{\mathcal{V}}
\newcommand{\Dub}{\mathcal{W}}
\newcommand{\Zed}{\mathcal{Z}}
\newcommand{\Exp}{\mathbb{E}}
\newcommand{\de}{\mbox{d}}
\newcommand{\wrt}{\,\mbox{d}}
\newcommand{\veczero}{\mathbf{0}}
\newcommand{\vecone}{\mathbf{1}}
\newcommand{\vecalpha}{\mbox{\boldmath$\alpha$}}
\newcommand{\vectheta}{\mbox{\boldmath$\theta$}}
\newcommand{\vecphi}{\mbox{\boldmath$\phi$}}
\newcommand{\vecPhi}{\mbox{\boldmath$\Phi$}}
\newcommand{\vecSigma}{\mbox{\boldmath$\Sigma$}}
\newcommand{\vecimath}{\mbox{\boldmath$\imath$}}
\newcommand{\cosech}{\mbox{cosech}\,}
\newcommand{\sign}{\mbox{sign}\,}
\newcommand{\trace}{\mbox{trace}\,}
\newcommand{\Inf}{\mbox{Inf}\,}
%\newcommand{\Ro}{R_0}
\DeclareMathOperator{\var}{var}
\DeclareMathOperator{\cov}{cov}

@@

\subsection{Measles importation risk results}
%%%%%%%%% TODO %%%%%%%%%%%%%%%%%%% BELOW 'RISK' TABLES and FIGURES %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%% CHECK UNITS FOR RISK ARE 'CASES PER MILLION TRAVELLERS PER YEAR' %%%%%%%%
%%% was annual incidence per million * # travellers per year %%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%% TODO %%%%%%%%%%%%%%%%%%% BELOW 'RISK' TABLES and FIGURES %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%% ADD UNITS FOR RISK TO CAPTIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{table}
<<results=tex,echo=FALSE>>=
latex(risk, file="", table.env=FALSE,rowname=NULL)
@
\caption{Risk of measles importation to New Zealand in 2013, estimated by 0--19 year old international and all New Zealander traveller numbers multiplied by measles incidence in the source or destination location, see also \autoref{table:nzrisk12} and \autoref{table:imrisk12}.}
\label{table:risk12}
\end{table}

\begin{table}
<<results=tex,echo=FALSE>>=
latex(nzrisk, file="", table.env=FALSE,rowname=NULL)
@
\caption{Indicator of risk of measles importation to New Zealand due to New Zealander travel in 2013, estimated by all traveller numbers multiplied by measles incidence in the source or destination location, see also \autoref{table:imrisk12} and \autoref{table:risk12}.}
\label{table:nzrisk12}
\end{table}

\begin{table}
<<results=tex,echo=FALSE>>=
latex(imrisk, file="", table.env=FALSE,rowname=NULL)
@
\caption{Indicator of risk of measles importation to New Zealand due to non-New Zealander 0--19 year old travel and immigration in 2013, estimated by traveller numbers multiplied by measles incidence in the source or destination location, see also \autoref{table:nzrisk12} and \autoref{table:risk12}.}
\label{table:imrisk12}
\end{table}

@@

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013totnp4.pdf}
\end{center}
\caption{Risk map for measles importation, based on measles incidence and non-New Zealander 0--19 year old and all ages of New Zealander travel figures, 2013. Dark grey indicates no data were available.}
\label{fig:risk12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013nznp4.pdf}
\end{center}
\caption{Risk map for measles importation from New Zealander international travel, based on measles incidence and travel figures, 2013. Dark grey indicates no data were available.}
\label{fig:nzrisk12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013np4.pdf}
\end{center}
\caption{Risk map for measles importation from 0--19 year old non-New Zealander international travel and immigration and measles incidence, 2013. Dark grey indicates no data were available.}
\label{fig:imrisk12}
\end{sidewaysfigure}

>>>>

\documentclass{article}
%\PassOptionsToPackage{draft}{graphicx} % draft without figures
\usepackage{longtable}
\usepackage{times}
\usepackage{hyperref}
\usepackage{tikz}
%\usepackage{bibunits}
\usepackage{natbib}
\usepackage{graphics}
\usepackage{amsmath}
\usepackage{indentfirst}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{eurosym}
\usepackage{todonotes}
\usepackage{subfig}
\usepackage{enumitem}
\usepackage{pdflscape}
\usepackage{booktabs}
\usepackage{array}
\usepackage{rotating}
\usepackage{threeparttable}
\usepackage{blindtext}
\usepackage{dcolumn}
\usepackage{tabularx}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage{caption2}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{placeins}
\usepackage{framed}
\usepackage{float}
\usepackage{authblk}
\usepackage[maxfloats=50]{morefloats}
\newcommand{\vecA}{\mathbf{A}}
\newcommand{\vecB}{\mathbf{B}}
\newcommand{\vecC}{\mathbf{C}}
\newcommand{\vecD}{\mathbf{D}}
\newcommand{\vecE}{\mathbf{E}}
\newcommand{\vecF}{\mathbf{F}}
\newcommand{\vecH}{\mathbf{H}}
\newcommand{\vecI}{\mathbf{I}}
\newcommand{\vecJ}{\mathbf{J}}
\newcommand{\vecK}{\mathbf{K}}
\newcommand{\vecM}{\mathbf{M}}
\newcommand{\vecN}{\mathbf{N}}
\newcommand{\vecP}{\mathbf{P}}
\newcommand{\vecQ}{\mathbf{Q}}
\newcommand{\vecS}{\mathbf{S}}
\newcommand{\vecT}{\mathbf{T}}
\newcommand{\vecW}{\mathbf{W}}
\newcommand{\vecZ}{\mathbf{Z}}
\newcommand{\vecb}{\mathbf{b}}
\newcommand{\vecc}{\mathbf{c}}
\newcommand{\vece}{\mathbf{e}}
\newcommand{\vecf}{\mathbf{f}}
\newcommand{\vecg}{\mathbf{g}}
\newcommand{\vech}{\mathbf{h}}
\newcommand{\veci}{\mathbf{i}}
\newcommand{\vecr}{\mathbf{r}}
\newcommand{\vecu}{\mathbf{u}}
\newcommand{\vecv}{\mathbf{v}}
\newcommand{\vecw}{\mathbf{w}}
\newcommand{\vecx}{\mathbf{x}}
\newcommand{\vecy}{\mathbf{y}}
\newcommand{\vecz}{\mathbf{z}}
\newcommand{\Ach}{\mathcal{H}}
\newcommand{\Ell}{\mathcal{L}}
\newcommand{\En}{\mathcal{N}}
\newcommand{\Pe}{\mathcal{P}}
\newcommand{\Ro}{\mathcal{R}_0}
\newcommand{\Rc}{\mathcal{R}_c}
\newcommand{\Pv}{\mathcal{P}_v}
\newcommand{\Rr}{\mathcal{R}}
\newcommand{\Qu}{\mathcal{Q}}
\newcommand{\Te}{\mathcal{T}}
\newcommand{\Ve}{\mathcal{V}}
\newcommand{\Dub}{\mathcal{W}}
\newcommand{\Zed}{\mathcal{Z}}
\newcommand{\Exp}{\mathbb{E}}
\newcommand{\de}{\mbox{d}}
\newcommand{\wrt}{\,\mbox{d}}
\newcommand{\veczero}{\mathbf{0}}
\newcommand{\vecone}{\mathbf{1}}
\newcommand{\vecalpha}{\mbox{\boldmath$\alpha$}}
\newcommand{\vectheta}{\mbox{\boldmath$\theta$}}
\newcommand{\vecphi}{\mbox{\boldmath$\phi$}}
\newcommand{\vecPhi}{\mbox{\boldmath$\Phi$}}
\newcommand{\vecSigma}{\mbox{\boldmath$\Sigma$}}
\newcommand{\vecimath}{\mbox{\boldmath$\imath$}}
\newcommand{\cosech}{\mbox{cosech}\,}
\newcommand{\sign}{\mbox{sign}\,}
\newcommand{\trace}{\mbox{trace}\,}
\newcommand{\Inf}{\mbox{Inf}\,}
%\newcommand{\Ro}{R_0}
\DeclareMathOperator{\var}{var}
\DeclareMathOperator{\cov}{cov}

@@

\subsection{Measles importation risk results}

@@

\begin{table}
<<results=tex,echo=FALSE>>=
latex(risk, file="", table.env=FALSE,rowname=NULL)
@
\caption{Risk of measles importation in cases per million travellers per year to New Zealand in 2013, estimated by 0--19 year old international and all New Zealander traveller numbers multiplied by measles incidence in the source or destination location, see also \autoref{table:nzrisk12} and \autoref{table:imrisk12}.}
\label{table:risk12}
\end{table}

\begin{table}
<<results=tex,echo=FALSE>>=
latex(nzrisk, file="", table.env=FALSE,rowname=NULL)
@
\caption{Indicator of risk of measles importation in cases per million travellers per year to New Zealand due to New Zealander travel in 2013, estimated by all traveller numbers multiplied by measles incidence in the source or destination location, see also \autoref{table:imrisk12} and \autoref{table:risk12}.}
\label{table:nzrisk12}
\end{table}

\begin{table}
<<results=tex,echo=FALSE>>=
latex(imrisk, file="", table.env=FALSE,rowname=NULL)
@
\caption{Indicator of risk of measles importation in cases per million travellers per year to New Zealand due to non-New Zealander 0--19 year old travel and immigration in 2013, estimated by traveller numbers multiplied by measles incidence in the source or destination location, see also \autoref{table:nzrisk12} and \autoref{table:risk12}.}
\label{table:imrisk12}
\end{table}

@@

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013totnp4.pdf}
\end{center}
\caption{Risk map for measles importation in cases per million travellers per year, based on measles incidence and non-New Zealander 0--19 year old and all ages of New Zealander travel figures, 2013. Dark grey indicates no data were available.}
\label{fig:risk12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013nznp4.pdf}
\end{center}
\caption{Risk map for measles importation in cases per million travellers per year from New Zealander international travel, based on measles incidence and travel figures, 2013. Dark grey indicates no data were available.}
\label{fig:nzrisk12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013np4.pdf}
\end{center}
\caption{Risk map for measles importation in cases per million travellers per year from 0--19 year old non-New Zealander international travel and immigration and measles incidence, 2013. Dark grey indicates no data were available.}
\label{fig:imrisk12}
\end{sidewaysfigure}
